Supplementary Informations to\\ Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels

### 2016-10-24 ion_pairing_SI.tex
NMR integration at n=70

\begin{figure}
\includegraphics[width=\textwidth]{POH_1H_NMR.png}
\caption{1H NMR of POH in deuterated methanol, with signal attribution. Calibration of the integrals intensity, relative to the distinct chain-end signals (a and b, 6 protons each), allows us to determine polymer chain length $n$ (here, considering integration of signal d, $n=63$)}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{POH_1H_NMR.png}
\caption{1H NMR of POH in deuterated methanol, with signal attribution. Calibration of the integrals intensity, relative to the distinct chain-end signals (a and b, 6 protons each), allows us to determine polymer chain length $n$ (here, considering integration of signal d,  $n=69-70$, $Mn=\SI{8335}{\dalton}$)}
\end{figure}
